ProteInfer: deep networks for protein functional inference

### 2021-09-20 latex/draft3.tex
Change PDF splitting technique, bump PDF
Abstract

\begin{abstract}
Predicting the function of a protein from its amino acid sequence has been a long-standing challenge for the bioinformatics community. Standard approaches use sequence alignment to compare a query sequence either to thousands of models of protein families or to large databases of individual protein sequences. In our work, we instead employ deep convolutional neural networks to directly predict a variety of protein functions - EC numbers and GO terms - directly from an unaligned amino acid sequence. This approach provides precise predictions which complement alignment-based methods, and the computational efficiency of a single neural network permits novel and lightweight software interfaces. In response, we have provided an in-browser graphical interface for protein function prediction in which all computation is performed on the user's personal computer with no data uploaded to remote servers. Moreover, these models place full-length amino acid sequences into a generalised functional space, facilitating downstream analysis and interpretation. To read the interactive version of this paper, please visit \url{https://google-research.github.io/proteinfer/}.
\end {abstract}

@@

%startleaveout
\section*{Bibliography}
\bibliography{../bibliography}
\onecolumn
\newpage
%stopleaveout
\include{supplement}
%startleaveout

>>>>

\begin{abstract}
Predicting the function of a protein from its amino acid sequence has been a long-standing challenge for the bioinformatics community. Standard approaches use sequence alignment to compare a query sequence either to thousands of models of protein families or to large databases of individual protein sequences. Here we instead employ deep convolutional neural networks to directly predict a variety of protein functions -- EC numbers and GO terms -- directly from an unaligned amino acid sequence. This approach provides precise predictions which complement alignment-based methods, and the computational efficiency of a single neural network permits novel and lightweight software interfaces. In response, we have provided an in-browser graphical interface for protein function prediction in which all computation is performed on the user's personal computer with no data uploaded to remote servers. Moreover, these models place full-length amino acid sequences into a generalised functional space, facilitating downstream analysis and interpretation. To read the interactive version of this paper, please visit \url{https://google-research.github.io/proteinfer/}.
\end {abstract}

@@

%startleaveout
\section*{Bibliography}
\bibliography{../bibliography}
\onecolumn
\newpage
%stopleaveout
\include{the_supplement}
%startleaveout
